\documentclass[12pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=red,
    filecolor=red,
    urlcolor=red,
}

\author{The DEV team}
\title{Exercise DEV2}


\begin{document}
	\maketitle

	\section{Introduction}
	    In this series of exercises you will be guided through the assignments 1 and 2 step by step.
	    The assignments have been broken up in the relevant parts; an exercise for each part.
	    The exercises each contain 2 parts: in the first one you will focus on the main concept that is related to this exercise, in the second part you will integrate that concept into a pygame application.
	    In this way you will have an aditional concrete example of the concepts you have seen in the lessons with respect to the assignments.
	    And you will learn to handle the complexity of a larger application.

%	    \paragraph{}
%	    Let's start with a breakdown of the application into course pieces.


	\section{Exercise 1 - make a car move}
        As said in the introduction. you will first focus on a relevant part.
        Assignment 1 is about cars in a city.
        We already gave you the city, so let's focus on the car.

        The relevant concepts are \href{https://github.com/hogeschool/INFDEV02-2/raw/master/Slides/Lecture%20I%20-%20data%20structures.pdf}{classes} and \href{https://github.com/hogeschool/INFDEV02-2/raw/master/Slides/Lecture%20V%20-%20methods.pdf}{methods} (those are links to the slides).
        In (very, very) short: A class is a blueprint which defines what data can be stored.
        An object can be instantiated, and can then store the data you want in attributes.
        Methods can be used to modify that data.

        \paragraph*{Console version}
			\begin{itemize}
				\item Build a \texttt{Car} class;
				\item Add the attribute \texttt{Position}, which will be a simple integer;
				\item Add the \texttt{Move} method that increments the position by one;
				\item Make a test program that initialises the car and moves it ten times; print the position of the car on the console at every step.
			\end{itemize}

		\paragraph*{Pygame version}
			\begin{itemize}
			    \item Get a template to kick-start your pygame application.
			    For example from \href{http://openbookproject.net/thinkcs/python/english3e/pygame.html}{here}.
			    Delete code you don't need, so you have a relative clean application to start with.
			    \item Draw -- Now add a shape or picture that will represent the car.
			        For now you can put it in the game loop.
			        Play around a bit with its parameters and make shure you understand how you can move the 'car'.
			    \item Now add the \texttt{Car} class from part 1.
			    \item Instantiate a car-object.
			    \item From within the gameloop, call the move-method on the car
			    \item Now use the car-position to change where the car is drawn on the screen.
			\end{itemize}



	\section{Exercise 2 - make a list of cars move}
	    In the assignment you will have more than one car.
	    These multiple cars need to be stored in a way that makes it easy to use all these cars programatically.
	    For this, we've introduced \href{https://github.com/hogeschool/INFDEV02-2/raw/master/Slides/Lecture%20II%20-%20lists.pdf}{Lists} in the lessons.
	    In a list you typically store a lot of objects of the same type (but, it is possible to store any type).
	    In this exercise you will combine the Car-objects with lists.

		\paragraph*{Console version}
			\begin{itemize}
				\item Build the \texttt{Node} and \texttt{Empty} classes;
				\item Add the usual attributes \texttt{IsEmpty}, \texttt{Head}, and \texttt{Tail} to the classes;
				\item Make a test program that
				 \begin{itemize}
				    \item initialises a list of cars,
				    \item moves each of them ten times,
				    \item print the position of each car on the console at every step.
			    \end{itemize}
			\end{itemize}

		\paragraph*{Pygame version}
		    Expand on the pygame application from exercise 1.

			\begin{itemize}
				\item Add a \texttt{VerticalPosition} attribute to the car, so that each car has a different vertical position to distinguish it on the screen;
				\item Use the list of cars you just implemented to draw a pygame screen where various cars move from the left to the right of the screen.
			\end{itemize}

	\section{Exercise 3 - moving along checkpoints}
	    In the assignments the cars will not move along positions based on coordinates, but positions based on \textit{tiles} are used.
	    In this exercise we will focus on that concept, however we will use a slightly different example: metro's and metro stations.
	    Our metro is always at a metro station. It can travel between 2 neighbouring stations, but we will not store any positions in between 2 stations.

		\paragraph*{Console version}
			\begin{itemize}
				\item Make a \texttt{Station} class,
                        which contains a \texttt{Position} attribute and a \textt{Name};
                        for example: Station(Position(10,40), "Kralinse zoom")
				\item Make a list of stations;
				\item Make a \textt{Metro} class,
                        which has an attribute \texttt{CurrentStation} and a method \textt{Move}.
				\item The \texttt{CurrentStation} will store a reference to a node in the list of checkpoints;
				\item In the \texttt{Metro} class, the \texttt{Move} method changes position to the \texttt{Tail}, which is the next checkpoint;
				\item Make a test program that initialises a list of metro's, and moves them until they all reach the final checkpoint; print the position of each metro (which is now a checkpoint) on the console at every step.
			\end{itemize}

		    Let's reflect on what you did in the part of the exercise. The metro (or car) still stores its position, however that position is now abstracted away into a station object. Which has the advantage that you can reason about station "kralinse zoom" for example, instead of (10, 40).
		    Station still stores its position in terms of coordinates (10,40), because that is important information.
		    Stations are connected to each other by the linked list. a Node's head (containing station "kralingse zoom") is connected to the tail (containing it's neighbour "Capelse brug")

		\paragraph*{Pygame version}
			\begin{itemize}
				\item Draw a pygame screen with the Stations and the Metro's;
				\item The various metro move from one Station to the other.
			\end{itemize}

	\section{Exercise 4 - crossings}
		\paragraph*{Console version}
			\begin{itemize}
				\item Make a \texttt{Node2D} class, which contains attributes \texttt{TailLeft}, \texttt{TailRight}, \texttt{TailUp}, \texttt{TailDown}, and \texttt{Final}; this is effectively the same as a list but with four possible choices for the \texttt{Tail} (we call this a \textbf{matrix});
				\item Make a series of checkpoints and put them into \texttt{Node2D}'s;
				\item In the \texttt{Car}, the \texttt{Position} will now be a reference to a \texttt{Node2D} in the matrix of checkpoints;
				\item In the \texttt{Car}, the \texttt{Move} method changes position to one of the \texttt{Tail}s, which is the next chosen checkpoint; the choice can be random;
				\item Make a test program that initialises a list of cars, and moves them until they all reach a specific checkpoint with \texttt{Final == True}; print the position of each car (which is now a checkpoint) on the console at every step.
			\end{itemize}
			
		\paragraph*{Pygame version}
			\begin{itemize}
				\item Draw a pygame screen with the checkpoints and the cars;
				\item The various cars move from one checkpoint to the other (like the cars in the city assignment).
			\end{itemize}

	\section{Exercise 5 - bikes}
		\paragraph*{Console version}
		\begin{itemize}
			\item Make a \texttt{Bike} class that has the \texttt{Move} method just like the car;
			\item \texttt{Bike}'s are fast, so the bike moves by two tiles at a time;
			\item Add a \texttt{PrintPosition} method to the \texttt{Car} and the \texttt{Bike}, which prints where the vehicle is;
			\item Make a test program that initialises a list contains a mixture of cars and bikes, and moves them until they all reach a specific checkpoint with \texttt{Final == True}; print the position of each car or bike (which is now a checkpoint) on the console at every step.
		\end{itemize}
		
		\paragraph*{Pygame version}
		\begin{itemize}
			\item Add a \texttt{Draw} method to the \texttt{Car} and the \texttt{Bike}, which draws where the vehicle is with the proper texture; the texture is also added as an attribute of both \texttt{Car} and \texttt{Bike};
			\item Draw a pygame screen with the checkpoints, the bikes and the cars;
			\item The various cars and bikes move from one checkpoint to the other (like the cars and boats in the city assignment).
		\end{itemize}
	

\end{document}
