\documentclass{beamer}
\usetheme[hideothersubsections]{HRTheme}
\usepackage{beamerthemeHRTheme}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[space]{grffile}
\usepackage{listings}
\lstset{language=C,
basicstyle=\ttfamily\footnotesize,
mathescape=true,
breaklines=true}
\lstset{
  literate={ï}{{\"i}}1
           {ì}{{\`i}}1
}
\usepackage{color}
\newcommand{\red}[1]{
\textcolor{red}{#1}
}
\newcommand{\ts}{\textbackslash}

\title{Standard collections library}

\author{TEAM INFDEV}

\institute{Hogeschool Rotterdam \\ 
Rotterdam, Netherlands}

\date{}

\begin{document}
\maketitle

\SlideSection{Introduction}
\SlideSubSection{Lecture topics}
\begin{slide}{
\item Building one's collections is often not needed
\item Most modern languages couple a standard library with the runtime
\item In this lecture we shall list the various built-in collections of Python ($\geq 3$)
}\end{slide}

\SlideSection{Problem discussion}
\SlideSubSection{Introduction}
\begin{slide}{
\item How do we represent collections of data in Python?
\item What sort of collections are available?
\item What properties does each collection offer?
}\end{slide}

\begin{slide}{
\item Collections are not always straightforward \textbf{bags} of data
\item Collections should be thought of as \textbf{bags with structure}
}\end{slide}

\SlideSubSection{Bags?}
\begin{slide}{
\item A bag of data contains multiple values
\item The size of the bag is usually variable
\item Elements may be accessed via some dynamic mechanism
\begin{itemize}
\item For example, \textit{find the third element}
\end{itemize}
}\end{slide}

\SlideSubSection{Bags \textbf{with structure}?}
\begin{slide}{
\item Structure of data refers to how data is stored
\item There are \textbf{a lot} of possible structures of data
\begin{itemize}
\item 
\end{itemize}
\item We cannot really cover them all, we shall just brush the surface
}\end{slide}

\SlideSubSection{Examples}
\begin{slide}{
\item ...
}\end{slide}

\SlideSection{General idea}
\SlideSubSection{Introduction}
\begin{slide}{
\item How are we going to solve the problem?
}\end{slide}

\SlideSubSection{Description}
\begin{slide}{
\item What are the aspects of the solution?
}\end{slide}

\SlideSection{Technical details}
\SlideSubSection{Introduction}
\begin{slide}{
\item How is this done in Python?
}\end{slide}

\SlideSubSection{Syntax and semantics}
\begin{slide}{
\item How is this done in Python?
}\end{slide}

\SlideSubSection{Examples}
\begin{slide}{
\item Example instances of the solution
\item Code samples
\item Steps in the memory model and accompanying discussion in class
}\end{slide}

\SlideSection{Conclusion}
\SlideSubSection{Lecture topics}
\begin{slide}{
\item What problem did we solve today, and how?
}\end{slide}

\begin{frame}{This is it!}
\center
\fontsize{18pt}{7.2}\selectfont
The best of luck, and thanks for the attention!
\end{frame}

\end{document}

\begin{slide}{
\item ...
}\end{slide}

\begin{frame}[fragile]
\begin{lstlisting}
...
\end{lstlisting}
\end{frame}
